### 2014-10-23 Docs/managing_jobs/managingjobs.tex
add some Blue Waters info

@@

>>>>

\subsection{Monitoring Allocations}

The {\tt showusage} and {\tt showusage -f} commands give an
overview of the usage.

@@

\section{Using Blue Waters}

\subsection{Overview}

Each node has 2 compute units, and a compute unit has 16 integer / 8
floating point cores.  They suggest you run using all the integer
cores.  Furthermore, each compute unit is separated into 2 NUMA nodes.

A recommended configuration is:

\subsection{BW Compilers}

The Cray compilers are the default on blue waters, and version
8.3.3 works well with \maestro.

\subsection{Monitoring Allocations}

The {\tt usage} command will list your usage and {\tt usage -P {\em account}} will
list the usage for all users on an account.
